### 2013-08-28 thesis/src/chapters/chapter-1.tex
Remove duplicated txt and add figure source

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-1/public-cloud-services-market-size}
  \end{center}
  \caption{Public Cloud Services Market Size, 2010-2016 (forecast)}
  \label{ch1:public-cloud-services-market-size}
\end{figure}

@@

\section{Impact}
We hope that the concept of representing each level of an autoscaling subsystem as an autonomic one can be thought-provoking for cloud computing scientists.  What is more, we believe that our successful attempt to implement a simplified variant of an InterCloud architecture will cause its gain in interest and popularity. 
Finally, we consider the ideas contained in this work be beneficial to the OpenNebula ecosystem as they provide insights into the ways Quality of Service can be ensured:
\begin{itemize}
  \item implementing autoscaling capabilities
  \item designing \emph{cloud infrastructure} in accordance with InterCloud architecture
\end{itemize}
What is more, we believe that our successful attempt to implement a simplified variant of an InterCloud architecture will cause its gain in interest and popularity. And finally, the idea of representing each level of an autoscaling subsystem as an autonomic one can be thought-provoking for cloud computing scientists.

>>>>

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-1/public-cloud-services-market-size}
  \end{center}
  \caption{Public Cloud Services Market Size, 2010-2016 (forecast). Source: \textit{Gartner, 08/2012}}
  \label{ch1:public-cloud-services-market-size}
\end{figure}

@@

\section{Impact}
We hope that the concept of representing each level of an autoscaling subsystem as an autonomic one can be thought-provoking for cloud computing scientists.  What is more, we believe that our successful attempt to implement a simplified variant of an InterCloud architecture will cause its gain in interest and popularity. 
Finally, we consider the ideas contained in this work be beneficial to the OpenNebula ecosystem as they provide insights into the ways Quality of Service can be ensured:
\begin{itemize}
  \item implementing autoscaling capabilities
  \item designing \emph{cloud infrastructure} in accordance with InterCloud architecture
\end{itemize}
